### 2018-09-24 VV556/HW2/submission.tex
add part of proof

\section{Exercis2.1}
	\begin{enumerate}
		\item 
			\begin{proof}
				\begin{equation}
					\begin{aligned}
						RHS & = \frac{1}{4} (||x+y||^2  - ||x-y||^2)\\
						    & = \frac{1}{4} (<x+y, x+y> - <x-y, x-y>)\\
						    & = \frac{1}{4} (<x+y, x> + <x+y, y> - <x-y, x> - <x-y, -y>)\\
						    & = \frac{1}{4} (\overline{<x, x+y>} + \overline{<y, x+y>} - \overline{<x, x-y>} + \overline{<y, x-y>})\\
						    & = \frac{1}{4} (\overline{<x, x>} + \overline{<x, y>} + \overline{<y, x>} + \overline{<y, y>} - \overline{<x, x>} + \overline{<x, y>} + \overline{<y, x>} - \overline{<y, y>})\\
						    & = \frac{1}{2}(\overline{<x,y>} + \overline{<y, x>})\\
						    & = \frac{1}{2}(<x, y> + <y, x>)\\
						    & = <x, y> = LHS
					\end{aligned}
				\end{equation}
				The last line is valid as the inner-product is defined on real space s.t. $<x, y>=<y, x>$.
			\end{proof}
		\item 
			\begin{proof}
				As have been proved aboved
				\begin{equation}
					\begin{aligned}
						   & \frac{1}{4} (||x+y||^2  - ||x-y||^2)\\
						=  & \frac{1}{2}(<x, y> + <y, x>)
					\end{aligned}
				\end{equation}
				Also, replace $y$ with $iy$ yields
				\begin{equation}
					\begin{aligned}
						  & \frac{i}{4} (||x+iy||^2  - ||x-iy||^2)\\
						= & \frac{i}{2} (<x, iy> + <iy, x>)\\
						= & \frac{i}{2} (i<x, y> + \overline{i}<y, x>)\\
						= & \frac{1}{2} (-<x, y> + <y,x>)
					\end{aligned}
				\end{equation}
				Thus
				\begin{equation}
					\begin{aligned}
						RHS & = \frac{1}{4} (||x+y||^2  - ||x-y||^2) - \frac{i}{4} (||x+iy||^2  - ||x-iy||^2)\\
						    & = \frac{1}{2}(<x, y> + <y, x>) - \frac{1}{2} (-<x, y> + <y,x>)\\
						    & = <x, y> = LHS
					\end{aligned}
				\end{equation}
			\end{proof}
		\item 
			\begin{proof}
				\begin{equation}
					\begin{aligned}
						LHS & = ||x+y||^2 + ||x-y||^2\\
						    & = <x+y, x+y> + <x-y, x-y>\\
						    & = <x+y, x> + <x+y, y> + <x-y, x> - <x-y, y>\\
						    & = \overline{<x, x+y>} + \overline{<y, x+y>} + \overline{<x, x-y>} - \overline{<y, x-y>}\\
						    & = \overline{<x, x>} + \overline{<x, y>} + \overline{<y, x>} + \overline{<y, y>} + \overline{<x, x>} - \overline{<x, y>} - \overline{<y, x>} + \overline{<y, y>}\\
						    & = 2(<x, x>+<y, y>)\\
						    & = 2(||x||^2 + ||y||^2) = RHS
					\end{aligned}
				\end{equation}
			\end{proof}	
		\item 
			\begin{proof}

			\end{proof}

		\item

>>>>

\section{Exercis2.1}
	\begin{enumerate}
		\item 
			\begin{proof}
				\begin{equation}
					\begin{aligned}
						RHS & = \frac{1}{4} (||x+y||^2  - ||x-y||^2)\\
						    & = \frac{1}{4} (<x+y, x+y> - <x-y, x-y>)\\
						    & = \frac{1}{4} (<x+y, x> + <x+y, y> - <x-y, x> - <x-y, -y>)\\
						    & = \frac{1}{4} (\overline{<x, x+y>} + \overline{<y, x+y>} - \overline{<x, x-y>} + \overline{<y, x-y>})\\
						    & = \frac{1}{4} (\overline{<x, x>} + \overline{<x, y>} + \overline{<y, x>} + \overline{<y, y>} - \overline{<x, x>} + \overline{<x, y>} + \overline{<y, x>} - \overline{<y, y>})\\
						    & = \frac{1}{2}(\overline{<x,y>} + \overline{<y, x>})\\
						    & = \frac{1}{2}(<x, y> + <y, x>)\\
						    & = <x, y> = LHS
					\end{aligned}
				\end{equation}
				The last line is valid as the inner-product is defined on real space s.t. $<x, y>=<y, x>$.
			\end{proof}
		\item 
			\begin{proof}
				As have been proved aboved
				\begin{equation}
					\begin{aligned}
						   & \frac{1}{4} (||x+y||^2  - ||x-y||^2)\\
						=  & \frac{1}{2}(<x, y> + <y, x>)
					\end{aligned}
				\end{equation}
				Also, replace $y$ with $iy$ yields
				\begin{equation}
					\begin{aligned}
						  & \frac{i}{4} (||x+iy||^2  - ||x-iy||^2)\\
						= & \frac{i}{2} (<x, iy> + <iy, x>)\\
						= & \frac{i}{2} (i<x, y> + \overline{i}<y, x>)\\
						= & \frac{1}{2} (-<x, y> + <y,x>)
					\end{aligned}
				\end{equation}
				Thus
				\begin{equation}
					\begin{aligned}
						RHS & = \frac{1}{4} (||x+y||^2  - ||x-y||^2) - \frac{i}{4} (||x+iy||^2  - ||x-iy||^2)\\
						    & = \frac{1}{2}(<x, y> + <y, x>) - \frac{1}{2} (-<x, y> + <y,x>)\\
						    & = <x, y> = LHS
					\end{aligned}
				\end{equation}
			\end{proof}
		\item 
			\begin{proof}
				\begin{equation}
					\begin{aligned}
						LHS & = ||x+y||^2 + ||x-y||^2\\
						    & = <x+y, x+y> + <x-y, x-y>\\
						    & = <x+y, x> + <x+y, y> + <x-y, x> - <x-y, y>\\
						    & = \overline{<x, x+y>} + \overline{<y, x+y>} + \overline{<x, x-y>} - \overline{<y, x-y>}\\
						    & = \overline{<x, x>} + \overline{<x, y>} + \overline{<y, x>} + \overline{<y, y>} + \overline{<x, x>} - \overline{<x, y>} - \overline{<y, x>} + \overline{<y, y>}\\
						    & = 2(<x, x>+<y, y>)\\
						    & = 2(||x||^2 + ||y||^2) = RHS
					\end{aligned}
				\end{equation}
			\end{proof}	
		\item 
			\begin{proof}
				As any norm induced by inner product should satisfy the parallelogram law, it's easy to show that the norm $||.||_\infty : f\mapsto \sup_{x\in [a, b]} |f(x)|$ on $C[a, b]$ can not be induced by any inner product since it does not satisfy the parallelogram law. For example, let
				\begin{equation}
					f(x) = \frac{x-a}{b-a}
				\end{equation}
				and
				\begin{equation}
					g(x) = (\frac{x-a}{b-a})^2
				\end{equation}
				then
				\begin{equation}
					||f+g|| = \max_{x\in[a, b]} |(f+g)(x)| = |(f+g)(b)| = 2
				\end{equation}
				\begin{equation}
					||f-g|| = \max_{x\in[a, b]} |(f-g)(x)| = |(f-g)(\frac{a+b}{2})| = \frac{1}{4}
				\end{equation}
				\begin{equation}
					||f|| = \max_{x\in[a, b]} |f(x)| = |f(b)| = 1
				\end{equation}
				\begin{equation}
					||g|| = \max_{x\in[a, b]} |g(x)| = |g(b)| = 1
				\end{equation}
				It's obvious that
				\begin{equation}
					||f+g||^2 + ||f-g||^2 = \frac{65}{4} \neq 2(||f||^2 + ||g||^2) = 4
				\end{equation}
			\end{proof}

		\item 
			Assume the norm satisfies the parallelogram law, that is
			\begin{equation}
				||x+y||^2 + ||x-y||^2 = 2(||x||^2 + ||y||^2)
			\end{equation}
			Let
			\begin{equation}
				<x, y> \triangleq \frac{1}{4}(||x+y||^2 - ||x-y||^2)
			\end{equation}
			it's left to prove that $<x, y>$ is an inner product.\\
			Firstly, $<x, y+z>$ can be expanded according to the definition as follows
			\begin{equation}
				\begin{aligned}
					<x, y+z> & = \frac{1}{4}(||x+y+z||^2 - ||x-(y+z)||^2)\\
					         & = \frac{1}{4}(||y+z+x||^2 - ||y+z-x||^2)
				\end{aligned}
			\end{equation}
			Since
			\begin{equation}
				||y+z+x||^2 + ||y-z+x||^2 = 2(||y+x||^2 + ||z||^2)
			\end{equation}
			Then
			\begin{equation}
				||y+z+x||^2 = 2(||y+x||^2 + ||z||^2) - ||y-z+x||^2
			\end{equation}
			Swap $y$ and $z$ yields
			\begin{equation}
				||x+y+z||^2 = 2(||z+x||^2 + ||y||^2) - ||z-y+x||^2
			\end{equation}
			Adding the two equations above and divided by 2 yields
			\begin{equation}
				||y+z+x||^2 = ||y||^2 + ||z||^2 + ||x+y||^2 + ||x+z||^2 -\frac{1}{2}(||y-z+x||^2 + ||z-y+x||^2)
			\end{equation}
			Replace $x$ with $-x$
			\begin{equation}
				||y+z-x||^2 = ||y||^2 + ||z||^2 + ||x-y||^2 + ||x-z||^2 -\frac{1}{2}(||y-z-x||^2 + ||z-y-x||^2)
			\end{equation}
			Hence
			\begin{equation}
				||y+z+x||^2 + ||y+z-x||^2 = (||x+y||^2 - ||x-y||^2) + (||x+z||^2 - ||x-z||^2)
			\end{equation}
			As
			\begin{equation}
				<x, y> = \frac{1}{4} (||x+y||^2 - ||x-y||^2)
			\end{equation}
			and
			\begin{equation}
				<x, z> = \frac{1}{4} (||x+z||^2 - ||x-z||^2)
			\end{equation}
			It's therefore can be concluded that
			\begin{equation}
				<x, y+z> = <x, y> + <x, z>
			\end{equation}
			Secondly,
